\documentclass[]{deedy-resume-openfont}
\usepackage{fancyhdr}
\usepackage{fontspec}
\usepackage{fontawesome}
 
\pagestyle{fancy}
\fancyhf{}
  
\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     LAST UPDATED DATE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\lastupdated

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     TITLE NAME
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\namesection{ZACH BELLAY}{ 
\fontspec[Path = fonts/century-gothic/]{GOTHIC}
%
\begin{large} \faGithubSquare \end{large}
\href{https://github.com/zachbellay/}{/zachbellay} \qquad 
%
\begin{large} \faEnvelope \end{large}
{\href{mailto:zbellay@scu.edu}{zbellay@scu.edu} \qquad
%
\begin{large} \faPhone \end{large} (425) 444-7070} \qquad
%
\begin{large} \faLinkedinSquare \end{large} \href{https://www.linkedin.com/in/zachbellay/}{/in/zachbellay} \qquad
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN ONE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{minipage}[t]{0.31\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EDUCATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Education} 
\runsubsection{Santa Clara University}
\location{Santa Clara, CA | June 2020}
M.S. in Computer Engineering \\
GPA: 3.400/4.0

\sectionsep

\runsubsection{Santa Clara University}
\location{Santa Clara, CA | June 2019}
B.S. in Computer Engineering \\
GPA: 3.257/4.0\\

\smallskip

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     COURSEWORK
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Coursework}
\runsubsection{Graduate}
\location{}{
Computer Vision I, II \\
Digital Signal Processing \\
ML \& DSP on FPGA \\
Computational Creativity \\
Adv. Operating Systems \\
Adv. Computer Architecture \\
%Mathematical Finance \\
%Secure Coding in C/C++ \\
}
\sectionsep

\vspace*{4pt}

\runsubsection{Undergraduate}
\location{}{
Data Science \\
Applied Machine Learning \\
%Probability \& Statistics \\
%Linear Algebra \\
Theory of Algorithms \\
Software Engineering \\
Computer Networks \\
Operating Systems \\
Computer Architecture \\
Web Infrastructure \\
}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SKILLS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Skills}
\runsubsection{LANGUAGES}
\location{}{
Python • C • C++ • MATLAB\\
JavaScript • HTML/CSS • Bash \\  
}

\quad

\runsubsection{MACHINE LEARNING \& COMPUTER VISION}
\location{}{

Keras • Scikit-learn • OpenCV \\  
Numpy • Pandas • Jupyter Notebook • Matplotlib 
}

\quad

\runsubsection{Backend \& Cloud}
\location{}{
Docker • Kubernetes • Helm\\
MongoDB • MySQL • InfluxDB  \\
AWS EC2 • Gunicorn • Flask
%\locationbold{Git:} Github, Bitbucket \\
%\locationbold{Python:} OpenCV, Boto3, Flask, sklearn \\
%\locationbold{AWS:} S3, EC2, Lightsail \\
%\locationbold{Arduino:} ArduinoJSON, WiFi, PID
}

\quad

\runsubsection{HARDWARE}
\location{}{
Raspberry Pi • Jetson Nano\\
Teensy 3.2/3.6 • Arduino Uno/Mega •
Soldering
}

\quad

\runsubsection{CAD}
\location{}{
Fusion 360 • Blender • 3D Printing\\



}

\sectionsep


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN TWO
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{minipage} 
\hfill
\begin{minipage}[t]{0.66\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EXPERIENCE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Experience}

\runsubsection{Ford Motor Company}
\descript{| Product Development Intern}
\location{Jun 2019 - Sep 2019 | Palo Alto, CA}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}%

\item Developed and deployed small sensor network from scratch using   Kubernetes, Docker, InfluxDB, Flask, Gunicorn, LoRa, Arduino, The Things Network, LoRaWAN, and Fusion 360.

\end{tightemize}
\sectionsep

\runsubsection{OnePointOne}
\descript{| Computer Vision Intern}
\location{Jan 2018 - Mar 2019 | San Jose, CA}
\begin{tightemize}
\item Created multi-camera IoT array to capture images of plants growing on a vertical plane.
\item Developed image processing pipeline to remove lens distortion and to perform image stitching.
\end{tightemize}
\sectionsep

\runsubsection{Ford Motor Company}
\descript{| Product Development Intern}
\location{Jun 2018 - Sep 2018 | Palo Alto, CA}
\begin{tightemize}%

\item Developed applications for Ford's "Arduino for cars."
 
\item Created vehicle crash data marketplace proof of concept using Ethereum blockchain and InterPlanetary File System.

\end{tightemize}
\sectionsep

%\runsubsection{Breakout Mentors}
%\descript{| Python Tutor}
%\location{Jan 2018 - Jun 2018 | Santa Clara, CA}
%\begin{tightemize}
%\item Tutored middle school students one-on-one on how to program video games in Python using PyGame.
%
%\end{tightemize}
%\sectionsep



\runsubsection{SCU Robotic Systems Lab}
\descript{| Software Engineering Intern}
\location{Jan 2017 - Sep 2017 | Santa Clara, CA}
\begin{tightemize}
\item Built system  to control indoor vertical farming prototype using JSON-based Raspberry Pi to Arduino serial protocol, secure RESTful API with Python Flask via TLS, and web interface for API.

\item Prototype was used in a pitch that resulted in \$1.4M seed funding.

\end{tightemize}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Projects
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Projects}
\runsubsection{Robust Moving Object Detection}
\location{}{June 2018 – May 2019 \\}
\begin{tightemize}
\item Developed and implemented robust moving object detection algorithm with Python for senior design project.
\item Paper accepted at SPIE Defense + Commercial Sensing Conference.

\end{tightemize}
\sectionsep

\textsc{\runsubsection{Fingerprint Matching}
\location{}{May 2019\\}
\begin{tightemize}
\item Compared SIFT, SURF, and CNN feature extraction methods for fingerprint matching on the SOCOFing fingerprint dataset.
\end{tightemize}}
\sectionsep

\runsubsection{"Self Driving" Fish Tank}
%\descript{| [In Progress]}
\location{}{June 2017 – Present \\}
\begin{tightemize}
\item Designed omnidirectional robot with mounted fish bowl in Fusion 360.
\item Developed drivers to capture goldfish position with OpenCV and translate into commands to drive robot.
\end{tightemize}
\sectionsep

%\textsc{\runsubsection{Bluetooth Mesh Network}
%\location{}{March 2018\\}
%\begin{tightemize}
%\item Created Bluetooth mesh network between Android devices to provide connectivity during network outages.
%\item Developed interface between Android devices and Raspberry Pi to act as a gateway to internet.
%\end{tightemize}}

%\textsc{\runsubsection{Fingerprint Matching }
%\location{}{March 2018\\}
%\begin{tightemize}
%\item Created Bluetooth mesh network between Android devices to provide connectivity during network outages.
%\item Developed interface between Android devices and Raspberry Pi to act as a gateway to internet.
%\end{tightemize}}

%\sectionsep

\section{Awards} 
\begin{tabular}{rll}
2019	     & 2\textsuperscript{nd} Place  & Ford Summer Intern Hackathon\\
2019	     & Best in Session & Senior Design Conference\\
2018	     & 1\textsuperscript{st} Place  & Ford Summer Intern Hackathon\\
2018	     & 2\textsuperscript{nd} Place  & Hack for Humanity\\
2016	     & 2\textsuperscript{nd} Place  & Google Games\\
\end{tabular}
\sectionsep

\end{minipage} 
\end{document}  \documentclass[]{article}
